New Computer Data-Science Set-up: Python (anaconda, pycharm), R (r-studio) and other Programs Installations

### 2020-01-03 nontex/install/linux/fn_vim.Rmd
VSCode with R and Linux Setup

" For LimeLight
" Color name (:help cterm-colors) or ANSI code
let g:limelight_conceal_ctermfg = 'gray'
let g:limelight_conceal_ctermfg = 240
" Color name (:help gui-colors) or RGB color
let g:limelight_conceal_guifg = 'DarkGray'
let g:limelight_conceal_guifg = '#777777'
" highlight line
let g:limelight_bop = '^.*$'
let g:limelight_eop = '\n'
let g:limelight_paragraph_span = 0

"""""""""""""""""""""""""""""""""""""""""""""""""
" UI Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" Keep cursor in the middle of the page, useful for editing text
set so=999
" Turn limelight on by default
" autocmd VimEnter * Limelight
" Turn Goyo on by default
autocmd VimEnter * Goyo
```

@@

# Vim Editing

Delete a line.

```{bash}
# select text with cursor, then d for delete
d
# delete until end of line, outside insert mode
D
```

@@

@@

@@

# Vim Set-Up

Use [one-dark atom theme](https://github.com/joshdick/onedark.vim), otherwise color hard to read.

```{bash}

```

>>>>

" For LimeLight
" Color name (:help cterm-colors) or ANSI code
let g:limelight_conceal_ctermfg = 'gray'
let g:limelight_conceal_ctermfg = 240
" Color name (:help gui-colors) or RGB color
let g:limelight_conceal_guifg = 'DarkGray'
let g:limelight_conceal_guifg = '#777777'
" highlight line
let g:limelight_bop = '^.*$'
" let g:limelight_eop = '\n'
let g:limelight_paragraph_span = 0

"""""""""""""""""""""""""""""""""""""""""""""""""
" UI Settings
"""""""""""""""""""""""""""""""""""""""""""""""""
" Keep cursor in the middle of the page, useful for editing text
set so=999
" Turn limelight on by default
" autocmd VimEnter * Limelight
" Turn Goyo on by default
autocmd VimEnter * Goyo
" autocmd VimEnter * AirlineToggle
" In Goyo, if airline is turned on, do nto show scratch area
" autocmd! User GoyoEnter nested set eventignore=FocusGained
" autocmd! User GoyoLeave nested set eventignore=
```

@@

@@

## Vim go to Spot in Text Quickly

```
# ESC
# Search for word
/abc
# esc
# next occurance of word
n
# last occurance
N
# first occurance overall
ggn
# last occurance overall
G
# clear search highlighting
:noh
```

back to previous point

```
~.
```

@@

## Vim Statistics

- word count: *g, ctrl+g*

@@

# Vim Set-Up Others

## Chromebook

pressing esc key is an issue, too far away. On chromebook, remap the search key which is in the spot of the caps lock key to esc. and remap the esc key to search key.

1. search for keyboard under settings
2. launcher to escape, and escape to launcher

### 2020-01-03 nontex/install/windows/fn_installations.Rmd
VSCode with R and Linux Setup

@@

###############################
# Add these to Windows PATH:
###############################
# C:/ProgramData/Anaconda3/Scripts
# C:/ProgramData/Anaconda3
```

@@

```{bash}
# # if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
conda update --all

@@

```{r}
# windows
python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
# linux
python ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py
python ~/PyFan/ProjectSupport/graph/subplot.py
```

@@

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
apm install project-manager
apm install sublime-style-column-selection

@@

```
# in powershell
# enter cmd
# type powershell in cmd to enter powershell from cmd
powershell
# permission
set-executionpolicy remotesigned -scope currentuser
# install
iwr -useb get.scoop.sh | iex
```

@@

In addition to Atom.

@@

- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.
### Sublime

@@

@@

- PDF Okular
    + Linux: *sudo apt-get install okular*
    + Windows: install okular from windows app store
- PDF Adobe Acrobat
    + go to adobe website, log in using fwang26@uh.edu
    + go to my account, choose view and download my apps, choose acrobat & PDF, download Acrobat DC
    + UH account can only be activated on two accounts at once, so need to kick other computers out temporarily potentially

>>>>

*note*: Github people seem to have slowed down updating Atom since microsoft acquisition

@@

###############################
# Add these to Windows PATH:
###############################
# C:\ProgramData\Anaconda3\Scripts
# C:\ProgramData\Anaconda3
```

@@

```{bash}
# if there are bugs
# conda clean --packages
# use conda-forge as main channel, more updated packages
conda config --get channels
conda config --add channels conda-forge
conda config --get channels
# remove conda-forge from channels (do so for main env install)
conda config --remove channels conda-forge
# normal update
conda update --all

@@

```{bash}
# windows
python "C:/Users/fan/PyFan/ProjectSupport/Testing/Numpy/Functions.py"
python "C:/Users/fan/PyFan/ProjectSupport/graph/subplot.py"
# linux
python ~/PyFan/ProjectSupport/Testing/Numpy/Functions.py
python ~/PyFan/ProjectSupport/graph/subplot.py
```

@@

```{bash}
# Once atom is installed, can use apm to install packages
apm install hydrogen
apm install project-manager
apm install sublime-style-column-selection
apm install minimap

# vim distraction free editing
apm install vim-mode-plus
apm install zen

@@

```{bash}
# in powershell
# enter cmd
# type powershell in cmd to enter powershell from cmd
powershell
# permission
set-executionpolicy remotesigned -scope currentuser
# install
iwr -useb get.scoop.sh | iex
```

@@

In addition to Atom, which is pretty slow, and harder to run on lower spec computers.

### VSCode

VSCode is much more light-weight than Atom, does not have hydrogen.

```{bash}
# Debian Install
curl https://packages.microsoft.com/keys/microsoft.asc | gpg --dearmor > microsoft.gpg
sudo install -o root -g root -m 644 microsoft.gpg /usr/share/keyrings/microsoft-archive-keyring.gpg
sudo sh -c 'echo "deb [arch=amd64 signed-by=/usr/share/keyrings/microsoft-archive-keyring.gpg] https://packages.microsoft.com/repos/vscode stable main" > /etc/apt/sources.list.d/vscode.list'
sudo apt-get install apt-transport-https
sudo apt-get update
sudo apt-get install code # or code-insiders

# Change Font (https://www.reddit.com/r/Crostini/comments/cesxr0/vscode_ui_and_fonts_too_small_heres_how_to_fix_it/)
# modify: /usr/share/applications/code.desktop
nvim /usr/share/applications/code.desktop
#replace this line: Exec=/usr/share/code/code --unity-launch %F
Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--unity-launch %F"
#replace this line: Exec=/usr/share/code/code --new-window %F
Exec=sommelier -X --scale=0.8 --dpi=160 /usr/share/code/code "--new-window %F"

# Open File
# low density mode to see cleary
code
```

Extensions to Download for VSCode:

2. [Microsoft Python Extension](https://marketplace.visualstudio.com/items?itemName=ms-python.python)

```{bash}
ext install ms-python.python
ext install latex-workshop
```

#### VSCode Shortcuts

- Open up Settings: *Ctrl + ,*
- Preview Markdown in VSCode: *Ctrl + Shift + V*
- Open up left pane: *Ctrl + B*
- Wrap Text: *alt + Z*, switch between wrap or not to save screen space for example.

#### VSCode Benefits

1. open a file, if have workspace where the file is in, automatically expand tree and show where file is on left pane.

#### VSCode and R

VSCode works pretty well it seems with Rmd files. Rmd files are useful to work through algorithm, examples in preparation for writing usable functions. Rstudio has been often very slow for me, and I generally feel like can not stretch around and work in RStudio IDE.

In Atom, Hydrogen works, but really only works with very basic line by line testing.

Using VSCode with RMD files seems much quicker, and there is room to breath.

1. Install R following R installation instructions.
2. Then install extension [R](https://marketplace.visualstudio.com/items?itemName=Ikuyadeu.r). Microsoft stopped supporting rmd in VSCode: [R Tools for Visual Studio](https://github.com/microsoft/RTVS)
3. properly set path (might have to call vscode from r env)
    + *r.rterm.linux*: */home/wangfanbsg75/anaconda3/envs/r_env/bin/R*
4. Run:
    - ctrl + enter to activate R terminal
    - VSCode 2019 allows for Knit Rmd: *Ctrl + Shift + K*
    - also can run code segment: select lines and *ctrl + enter*

#### VSCode and Latex

1. download [Latex Workshop](https://marketplace.visualstudio.com/items?itemName=James-Yu.latex-workshop)

@@

- Silently update file changes made in other editors: Settings, Preferences, MISC., File Status Auto Detection, Update Silently.

### Sublime

@@

```{bash}
# Sublime Linux
wget -qO - https://download.sublimetext.com/sublimehq-pub.gpg | sudo apt-key add -
sudo apt-get install apt-transport-https
echo "deb https://download.sublimetext.com/ apt/stable/" | sudo tee /etc/apt/sources.list.d/sublime-text.list
sudo apt-get update
sudo apt-get install sublime-text
# launch from terminal
subl
```

@@

- PDF Okular
    + Linux: *sudo apt-get install okular*
    + Windows: install okular from windows app store
    + Okular configure shortcuts: setting, configure shortcuts
    + Okular if menu bar lost: *Ctrl + m*
    + Okular comment pane: *F6*
    + Okular close left pane: *F7*
    + Okular full scrren: *Ctrl + Shift + F*
        * unlike acrobat, pdf allows for multiple scrrens
    + Okular 3 pages per row view:
        * view, overview
    + Automatic Update when PDF updated elsewhere
        * this is one of the key reasons to use okular, when I knit a Rmd file to PDF, the currently open Okular PDF file automatically updates and does not give file is open error like Acrobat.
    + Background color:
        * can easily change background color to non-white.
- PDF Adobe Acrobat
    + go to adobe website, log in using fwang26@uh.edu
    + go to my account, choose view and download my apps, choose acrobat & PDF, download Acrobat DC
    + UH account can only be activated on two accounts at once, so need to kick other computers out temporarily potentially
